### 2017-03-19 Manuscript/Cover letter.Rmd
Home edits

---
output: pdf_document
---

Dr Lewis G. Spurgin
School of Biological Sciences
University of East Anglia
Norwich
Norfolk NR4 7TJ
United Kingdom

Email: L.Spurgin@uea.ac.uk
Web: lewisspurgin.wordpress.com

@@

Two of our main faindings are particularly striking and will, we hope, be of interest to your readers. Firstly, we find that cohort effects are the most important drivers of variation in telomere length in the Seychelles warbler population. This has important ramifications for how studies of natural populations interpret variaiton in teloemre length, as these are often based on a single timepoint. Our data suggest that telomere dynamics at a single point in time may in fact be a snapshot of a temporally dynamic process.

@@

>>>>

---
output: 
  pdf_document:
header-includes: \usepackage{graphicx}
---

\begin{flushright}

\includegraphics{UEAlogo}

School of Biological Sciences\\*
University of East Anglia\\*
Norwich\\*
Norfolk NR4 7TJ\\* 
United Kingdom

L.Spurgin@uea.ac.uk\\*
lewisspurgin.wordpress.com

\end{flushright}

\bigskip

**19th March 2017**

\bigskip

@@

Two of our main findings are particularly striking and will, we hope, be of interest to your readers. Firstly, we find that cohort effects are the most important drivers of variation in telomere length in the Seychelles warbler population. This has important ramifications for how studies of natural populations interpret variation in telomere length, as these are often based on a single time point. Our data suggest that telomere dynamics at a single point in time may in fact be a snapshot of a temporally dynamic process.

@@

\bigskip
